---
title: "hourly_temperature_prep"
format: html
editor: visual
---

Read in the data Serena generated

```{r}

library(lubridate)
library(dplyr)
library(chillR)
library(lutz)
library(stringr)

data <- read.csv("data/data_for_hourly_temperature_prep.csv")
data$longitude <- data$longitude.x
data$latitude <- data$latitude.x
```

Add date, time, and latitude columns we need to infer hourly temperatures

```{r}

# filter out UTC datetimes so we keep local only
data <- data[!str_detect(as.character(data$datetime), "UTC"), ]

# add month, day, latitude, and local hour columns
dates <- as.Date(data$yday - 1, origin = "2021-01-01")
data$Month <- month(dates)
data$Day <- day(dates)
data$Latitude <- round(data$latitude)
data$local_hour <- hour(ymd_hms(data$datetime, tz = ""))
```

Generate hourly temperature dataframe

This dataframe includes the temperatures of MANY hours of the day for each observation, given the tmin, tmax, and latitude of that observation

```{r}

# save unique latitudes
uniq_lats <- unique(data$Latitude)

# subset and rename data for stack hourly temps
data_for_hourly <- data %>% select(c(year,tmin,tmax,Month,Day,Latitude,id))
colnames(data_for_hourly) <- c("Year","Tmin","Tmax","Month","Day","Latitude","ID")

# we loop through each unique latitude and apply stack_hourly_temps to the data in that latitude
hourly_temp_data <- data.frame()
for(lat in uniq_lats){
    new_data <- dplyr::filter(data_for_hourly,Latitude==lat)
    ids <- new_data$ID
    new_data <- new_data[,1:5]
    new_data <- stack_hourly_temps(new_data, latitude=lat)$hourtemps
    new_data$ID <- ids
    hourly_temp_data <- rbind(hourly_temp_data,new_data)
}

# we ultimately get a df containing the hourly temperature for each ID
hourly_temp_data <- hourly_temp_data %>% select(c(Temp,ID,Hour))
colnames(hourly_temp_data) <- c("hour_temperature","id","local_hour")
print(head(hourly_temp_data))
```

Bind hourly temperature data back onto original data

By merging by "local_hour" we bind only the temperature for the true local hour in which the observation occurred

```{r}

final_data <- merge(data, hourly_temp_data, by=c("id","local_hour"))
final_data <- final_data %>% select(c(id,datetime,local_hour,county,scientific_name,hour_temperature,color,latitude.x,longitude.x))
print(head(final_data))
plot(final_data$local_hour,final_data$hour_temperature)
```
